\huge Tor's Usability for Censorship Circumvention

### 2016-04-07 pets2017-paper/pets2017-paper.tex
limitations

\section{Limitations} 
{\color {red} our study was only run on windows machines. our participants were not motivated like real users would be in real environments to succeed, but also may have been too motivated since they were getting paid. We didn't intentionally test the cases in which the user is required to configure a custom bridge or proxy. Our users were recruited from one geographic location, and their first language is English.}

>>>>

\section{Limitations} 
The interface was only tested on windows machines, which were the only types of machines available machines in Xlab. The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems. Participants who are not accustomed to using Windows machines may have been slower than usual to complete the given task, but this effect should affect all of our conditions equally.

Our study was conducted in an inorganic setting, which can cause our participants to be under or over-motivated. Our participants had a monetary incentive  to connect to Tor, whereas as a real user in a censored environment would Tor to reach a particular website or service. Additionally, the presence of researchers may have placed social pressure to attempt connect for the whole duration of the session, when they would have given up if they were not in a laboratory setting.

We did not test cases in which the user is required to configure a custom bridge or proxy. Our participants were from one geographic location in the United States and are able to speak English.
